A thesis draft

### 2018-10-01 draft.tex
Add TCP session recreation

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been incapsulated by the MANO,
\todo{Not sure about this, please give it a check} making the whole
architecture indipendent from the protocol a particolar flux of data uses. To
achieve this, TUN/TAP\todo{Find out acronym} interfaces were used to deploy a
tunnel between VNFs, allowing them to pass packets encapsulated in UDP ones.

@@

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified).

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\end{document}

>>>>

The analysis of this topic revealed to be trivial: since internet has many
different protocols that would become infeasible to support all of them at the
same time, packet incapsulation present itself as the only faseable solution:
every packet incoming in the VNFs has already been incapsulated by the MANO,
\todo{Not sure about this, please give it a check - Not sure but I think that
it is not part of the MANO the encapsulation of the packets. Also I think that
the main purpose of UDP encapsulation is not to hide the protocol used on the
edges but 1) usa a ``quick protocol to exchange data among VNFs and 2) we are
hiding the path not the protocol itself. As we were discussing, we are creating
some sort of proxy, so the aim will be the same even if we support a plethora
of protocols.''} making the whole architecture indipendent from the protocol a
particolar flux of data uses. To achieve this, TUN/TAP
\todo{Find out acronym - EPKT? (Encapsulated PacKeT)}
interfaces were used to deploy a tunnel between VNFs, allowing them to pass
packets encapsulated in UDP ones.

@@

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified). TCP session recreation, instead, ``split'' the TCP session in two 
endpoints: an Ingress, that manage the connection with the client and an 
Egress, that communicate with the packet receiver. In order to achieve that, a 
session table needs to be established and continuously updated, while TCP 
headers need to be accordingly modified to allow data transmission through the 
Ingress and Egress points. TCP session recreation seems burdersome at the first 
sight, but it offers the flexibility to perform extensive packet manipulation: 
since the packet its recreated every time at the Ingress and Egress points, 
while in the Network Function Virtualization Infrastructure (NFVI), the 
original packet can be stripped of its headers (that could be saved in the 
session table) to slightly improve internal packet transmission. \todo{Insert 
TCP session recreation schema}

During the testbed development we first tried the TUN/TAP solution, that 
revealed to be not completely transparent and with major performance drawbacks 
(i.e. packet transmission in a LAN connection reached latencies of 50ms) 
\todo{Explain the constraint of point-to-point connections, while we need 
dynamic SFC)}

In TCP Splitting, instead, we split the path from sender and receiver dividing
the end-to-end TCP connection into a multi-overlay-hop path where to each hop
we have an independant TCP cconnection. Each segment that composes the whole
path can use different flavours of TCP, e.g. using different enhancement based
on the tipology of the connection (in case of satellite connection we TCP Hybla
can be used, HighSpeed TCP in case of optical fiber). That could cause
performance issues depending on the intermediate proxies that create the route:
it is the case, for example, when an intermediate node sends back a spoofed ACK
before the original packet is delivered to the real consegnee. In that senario,
the sender unaware of the proxy, will miscalculate the sending window based on
the too low RTT. Other problems of TCP splitting are reliability andd security:
breacking the end to end TCP logic: a server failure is may cause to an unaware
client to believe that all packets reach the destination.

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\paragraph{Openbaton}
\paragraph{SDN?}
\end{document}
